---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo=FALSE, messages=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(bonn)
```


# bonn 

The R package `bonn` provides functions to retrieve data from the [INKAR database](https://www.inkar.de/) maintained by the Federal Office for Building and Regional Planning (BBSR) in Bonn. The package uses an undocumented JSON API. 



### Installation 

You can install the package from Github using:  

```{r, eval = FALSE}
remotes::install_github("sumtxt/bonn", force=TRUE)
```


### Usage 

The main data-retrieving function is `get_data()`. It requires to specify which variable to retrieve and for which geography. By default this function retrieves the data for all available time points and for all available units of a named geography. 

For a list of available geographies (municipalities, disricts etc.), call `get_geographies()`. Then use `get_themes()` with the appropriate geography identifier to obtain a list of themes for which variables are available. Then call `get_variables()` for a list of available variables. Not all variables are available for every geography. Use the variable and geography identifier to call `get_data()`. To obtain a detailed description of a variable, call `get_metadata`.

List available themes for districts (Kreise):

```{r}
head( get_themes(geography="KRE") ) 
```

Indicators for theme "unemployment": 

```{r}
head( get_variables(theme="011", geography="KRE") ) 
```

Retrieve data and metadata on the unemployment variable: 

```{r}
head( get_data(variable='12', geography="KRE") ) 
```

### Notes 

- User reports suggest that some IDs of the database are not necessarily stable over time (see https://github.com/sumtxt/bonn/issues/1). 

### Complementary Packages 

* The R package `wiesbaden`  [github.com/sumtxt/wiesbaden](https://github.com/sumtxt/wiesbaden) provides functions to directly retrieve data from databases maintained by the Federal Statistical Office of Germany (DESTATIS) in Wiesbaden

* The R package AGS [github.com/sumtxt/ags](https://github.com/sumtxt/ags/) provides functions to work with the Amtlicher Gemeindeschlüssel (AGS), e.g. construct time series of statistics for Germany's municipalities and districts.
